Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-01 doc/PRF2022/PRF_main.tex
removed tabulararray package call
added references

\usepackage{todonotes}
\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{tabularx}
\usepackage{tabularray}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newcommand{\RomanNumeralCaps}[1]
\linenumbers

@@

\begin{abstract}
Active colloidal systems with non-equilibrium self-organization is a long-standing challenge in biology. To understand how hydrodynamic flow may be used
to actively control self-assembly of Janus particles (JPs),  we use a model recently developed for the many-body hydrodynamics of amphiphilic JPs suspended 
in a viscous background flow (JFM, 941, 2022). We investigate how various bilayer structures arise from tuning the hydrophobicity/hydrophilicity of the JPs. 
Focusing on three distributions of hydrophobicity we found JPs may assemble into uni-lamella, multi-lamella, and striated structures in a viscous fluid. 
Under a linear flow and a Taylor-Green mixing flow,  we use three measures to quantify the collective dynamics of JP particles under a background flow: 
(a) Free energy from the hydrophobic interactions between the JPs, (b) an order parameter for the ordering of JPs in terms of alignment of their directors, 
and (c) a strain parameter that captures the deformation in the assembly. We found the dynamics of these three measures correlate well with the hydrodynamics 
of JPs. These numerical provide insights into dynamic control of non-equilibrium active biological systems with similar self-organization.
% insert abstract here
\end{abstract}

@@

\todo[inline]{Here are some references that Yuan sent around in the last
few weeks}
\cite{KolevaRehage2012_SoftMatter}
\cite{GrandmaisonBrancherieSalasac2021_JFM}
\cite{MusselLewisBasserHorkay2022_PRM}
\cite{HuLongZangEHan2022_arxiv}
\cite{BoccardoPierreLouis2022_PRL}

\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
Janus particles are colloids with two surfaces of different properties such as hydrophobicity. For example, it is common for the surface of a Janus particle to
be partly hydrophilic and hydrophobic (polar and non-polar). In a viscous solvent Janus particles often self-assemble into structures with tunable functions for biomedical engineering applications \cite{GheisariSahfieeAbbasiEtAl2021_DMR,LiuYangHuangEtAl2016_Angew,LiWangYaoEtAl2019_Nanoscale}. Depending on the interactions between Janus particles and the surrounding viscous solvent, JPs self-assemble into oligomers of various geometries and sizes.

{\bf The following paragraph needs to be rephrased and inserted in the introduction.
"Dynamics offers yet another dimension of control that emerges naturally from the interactions between particles and fluid in colloidal matter. ....Such active colloidal systems show nonequilibrium self-organization with complexity rivaling that of biological systems such as living cells, bacterial baths, and animal flocks.....long-standing challenges such as the ``inverse" problem of creating a colloidal system that will self-assemble into a prescribed structure.....the framework of geometrical frustration, which has been used to explain dis-ordered systems, could be used to design new ones instead, through specific choices for the shapes or interactions of the particles....\cite{Manoharan2015_Science}"}

The many-body hydrodynamics of amphiphilic Janus particles (JP) suspended in a viscous fluid (at zero Reynolds number) has been studied using
boundary integral numerical simulations \cite{Fu2022_JFM}. Janus particles consist of both a hydrophobic and a hydrophilic surfaces. 
Immersed in a viscous solvent, the dynamics of a JP suspension results from the combination of long-range hydrodynamic interaction and non-local
interactions between JPs through the distribution of a hydrophobic potential (HAP). In a quiescent flow, numerical simulations of a 
JP suspension showed self-assembly into micelles and bilayers of JPs that provide an alternative means for computing the 
mechanical moduli of a colloidal membrane.

Under background flows, the hydrodynamics of a JP vesicle (a
self-enclosed bilayer of JPs) exhibit many familiar behaviors of a
vesicle \cite{Fu2022_JFM}: 
Elongation and alignment along the extensional direction, tank-treading, and rupture of a vesicle under shear flow.

In this work we take advantage of the flexibility of the model to examine the effects of boundary condition on JP surfaces that could be controlled based on the chemicals used in the experiments, for example.

@@

Without inertia, $(\uu, p)$ also satisfy the force-free and torque-free conditions.
This means that the force and torque from the hydrodynamic stress on each particle 
are in balance with the total
force and torque coming from the hydrophobic potential and repulsion \cite{Fu2022_JFM}.
To compute this balance, we define
the free energy\cite{Fu2022_JFM}
\begin{equation}
\label{eq:free_energy}
F = \gamma
\int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
\end{equation}
where $u(\xx,t)$ is as an order parameter for the structure of water,
$\rho$ is a decay length, and $\gamma$ is an interfacial tension.

The order parameter $u(\xx,t)$ is assumed to the minimizer of the free energy $F$ \cite{Fu20}.
Its governing equations $u(\xx,t)$ are a screened Laplace equation boundary value problem
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  \label{eq:SLbc}
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
The boundary condition $g$ encodes hydrophobic properties of the
particle-solvent interface.

@@

To get the force $\FF_i$ and torque $T_i$ on $\Gamma_i$ from the free energy,
we compute the variation of the domain of the free energy 
\eqref{eq:free_energy} subject to \eqref{eq:SL}-\eqref{eq:SLbc},
and obtain 
\begin{equation}
  \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
  - \frac{M}{\rho_0}
  \sum_{j \neq i}
  \frac{\aa_i - \aa_j}{|\aa_i - \aa_j|}
P'\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right)
  ,\quad
T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
\end{equation}
for $i = 1,\dots,N_b$ with particle outward normal $\nu$. The term 
$
\mathbf{T}
= \gamma \left[ \rho^{-1} u^2 \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
$
is the hydrophobic stress.
Repulsion is rotationally symmetric and does not contribute to the torque.
The derivation details are found in \citet{Fu20}.

@@

In BC (ii) with $b = 1$, the boundary data is everywhere positive.
It takes the maximum value $3a$ on the tail (red) and the
minimum value $a$ on the head side (yellow). 
Both sides of the Janus particle are hydrophobic but
more so on the $\alpha = 0$ side.  
Over a short time scale, these particles also self-assemble into bilayers. But unlike for  (i),
the heads are also hydrophobic and so in the long-time dynamics
these bilayers form multilamella structures.
The number of folds depends primarily on the number of particles.
Fig~\ref{fig:relax}(c), for example, shows a
multilamellar structure with four layers and one with two layers in the inset.

@@

To measure positional order, we use a number,
which we call the strain parameter, 
\begin{equation}
\label{eq:SP}
E = \frac{1}{N_b} \sum_{i=1}^{N_b}
\|\tfrac{1}{2}(\mathsf{F}_i^T \mathsf{F}_i - I)\|
\end{equation}
where $\mathsf{F}_i$ is an 
approximate deformation gradient at particle $i$.
The argument inside the Frobenius norm $\| \cdot \|$
is the Green-Lagrange strain tensor.
The motivation for  \eqref{eq:SP} is as follows.
For relatively weak background flow strengths, the near-equilibrium particle
configurations behave as an elastic solid.  There is a map $\ff(\xx,t)$
from the reference (equilibrium) configuration with $\ff(\aa_i(0),t) = \aa_i(t)$
for $i = 1,\dots,N_b$.  Using linear approximation,
\[
\aa_j(t) - \aa_i(t) = \ff(\aa_j(0),t) - \ff(\aa_i(0),t)
\approx \nabla \ff(\aa_i(0),t)(\aa_j(0) - \aa_i(0)).
\]
To approximate
the deformation gradient $\nabla \ff(\aa_i(0),t)$
we solved the overdetermined system 
\[
\aa_j(t) - \aa_i(t) = \mathsf{F}_i(\aa_j(0) - \aa_i(0)),\quad j = 1,\dots, N_b  
\]
for $\mathsf{F}_i$ by weighted least squares. The weights  
$w_i = \exp(-\|\aa_j(0) - \aa_i(0)\|/4c)$ with particle radius $c$
ensure that nearby particles contribute the most to the linear approximation at $\aa_i$.

@@

\section{Results}
\label{sec:results}
In this section, we subject the Janus particle structures to various background
flows.  The purpose of this study is to understand how self-assembled particles
respond to external fluid forcing.  We can then compare the results to guage
the effective properties of materials comprised of Janus particles as a function
of their amphiphilic properties.  
%%%

@@

%%%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure4.pdf}
  \end{center}
  \caption{
    \label{fig:Ves_shear}
The figure shows a single vesicle in a shear flow. Panels (a)-(c) are snapshots for $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
The streamlines are plotted in the background.
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
     }
\end{figure}
%
\citet{Fu2022_JFM} studied the hydrodynamics of a JP vesicle under a linear shear flow. 
Focusing on drawing analogies to hydrodynamics of a vesicle in continuum modeling
(such as tank-treading, bilayer slip and permeability),
our previous studies showed the existence of a critical shear
rate above which the JP vesicle ruptures. 
Based on the these early results, we
reinitialized the BC (i) configuration
in the form of a single, circular vesicle (rather than several bilayer components)
and illustrate how the three measures of structural deformation 
correlate to the dynamics of a JP vesicle.

@@

We calculated the vesicle area $A$ and length $L$ (initial area $A_0$, initial length $L_0$)
by averaging the area/length for the inner and outer leaflets.  
As shown in Fig~\ref{fig:BTG_Scale}(e),
the relative area $A/A_0$ decreases during the simulations, with a rate
depending nonmonotonically on $l$.  
The relative length $L/L_0$, however, is constant in $t$ for all cell sizes (Fig~\ref{fig:BTG_Scale}(e), inset).
This implies that the vesicle behaves as an inextensible, permeable membrane.
In previous work, \cite{Fu2022_JFM} determined the permeability constant of particle-based vesicles
in the context of shear background flow.

@@

\section{Discussion}
Our results were for $N_b = 60$.  This particle number was large enough for the JP to form
measurable structures while giving managable simulation times (days) on a single computing processor.
The simulation time for $N_b = 198$ in Fig. \ref{fig:relax} and Fig. \ref{fig:relax_energy}
was several weeks, and so we avoided simulations of this size for our results.
We used $N = 16$ grid points per particles for all simulations.  We performed a convergence study
and found that using $N = 16$ or $N = 24$ grid points per particle gave quantitavely indistinguishable
results.  The time courses consisted of $O(10^3)$ time steps with $\Delta = 0.2$ nm.

@@

In terms of fluid behavior,
the multilamellar (BC (ii)) structure behaves as shear thinning fluid
while the striated structure (BC (iii)) has a finite yield stress and
behaves as a Bingham plastic. 
Qualitatively, the strains for BC (ii) increases gradually 
with shear rate (Fig~\ref{fig:BC2_shear}(f)).
In contrast, the strains for BC (iii) are constant over a range of flow strengths
and then increase when the flow strengths are large enough
to deform the body (Fig~\ref{fig:BC3_shear}(f)).
To quantify this behavior, we form 
\[
\mu_{\text{sus}} = \frac{\dot \gamma}{\dot E} \mu
\]
as an effective dynamic viscosity of the suspension.
The numerator $\dot \gamma \mu$ gives the force per area provided by the solvent stresses. 
The strain rate $\dot E$ of the body is the slope of a linear fit to the strain curves e.g.,
in Fig~\ref{fig:BC2_shear}(f).

Calculated suspension viscosities are shown
in Table \ref{tbl:bcii_visc}.
The middle row gives the solid area fraction $\phi$. 
We observe that for the multilamellar structure,
$\mu_{\text{sus}}$ is decreasing
with increasing shear rate.  The predicted suspension viscosities 
are on the order of hundreds of times that of water, consistent with
measurements of noninteracting particle suspensions\cite{KONIJN201461}.
In the case of striated structures, viscosity is effectively infinite
for the lower two of the shear rates, and then drops to a finite value $\mu_{\text{sus}} = 60$ mPa s
when the shear rate reaches $0.15$ ns$^{-1}$.
\begin{table}
  \caption{Suspension viscosity $\mu_{\text{sus}}$ (mPa s) 
\label{tbl:bcii_visc}
}
\centering
\begin{tabularx}{0.7\textwidth}{c|X|X|X||X|X|X}
&\multicolumn{3}{c||}{BC (ii)} & \multicolumn{3}{c}{BC (iii)}\\
\hline
  $\dot \gamma$ & 0.05 & 0.10 \quad & 0.15 & 0.100 & 0.125 & 0.15\\
  \hline
  $\phi$ & 0.50 & 0.47 & 0.41 & 0.47 & 0.46 & 0.45 \\
  \hline
  $\mu_{\text{sus}} $ & 401 & 66 & 42 & 2.5e3 & 1.4e3 & 60\\
\hline
\end{tabularx}
\end{table}

We have not calculated suspension viscosities for the type (i) boundary condition,
because the viscosities of bilayer are in-plane and require fully three-dimensional
simulations to resolve.  Our previous work 
did calculate, however, an intermonolayer friction coefficient $b$
which is related but conceptually different than viscosity \cite{Fu2022_JFM}.

While increased flow strengths generally injected energy into the suspension,
the simulation results show that the unstructured bilayer 
actually increases orientational order and has somewhat lower free energy 
under low shear rates (Fig~\ref{fig:BC1_shear}(d,f)).
This effect suggests that in amphiphilic suspensions,
it might be possible decrease the excess area of the system 
by subjecting the suspension to a moderate shear flow.
Not all background flows produce this effect, as it was not
observed in the TG background flow case (Fig~\ref{fig:BC1_TG}).

@@

\section{Conclusion}
\label{sec:conclusion}

>>>>

\usepackage{todonotes}
\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{tabularx}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newcommand{\RomanNumeralCaps}[1]
\linenumbers

@@

\begin{abstract}
  Active colloidal systems with non-equilibrium self-organization
  is a long-standing challenging area in biology.
  To understand how hydrodynamic flow may be used to actively
  control self-assembly of Janus particles (JPs), we use a model
  recently developed for the many-body hydrodynamics of amphiphilic
  JPs suspended in a viscous background flow (JFM, 941, 2022).
  We investigate how various bilayer structures arise from tuning
  the hydrophobic properties of the JP-solvent interface.
  Focusing on a simple tuing of the hydrophobicity distribution,
  we found
  JPs assembled into uni-lamella, multi-lamella and striated
  structures.  To introduce dynamics, we include a linear shear flow and a
  Taylor-Green mixing flow, and measure the
  collective dynamics of JP particles in terms of their 
  (a) free energy from the hydrophobic interactions between the JPs,
  (b) order parameter for the ordering of JPs in terms of alignment of their directors, 
  and (c) strain parameter that captures the deformation in the assembly.
  We characterized the effective material proporties of the JP structures
  and found that the uni-lamellar structures increases orientation order under
  shear flow, the multilamellar structure behaves as a shear thinning fluid,
  and the striated structure possesses a finite yield stress.  
  These numerical result provide insights into dynamic control of
  non-equilibrium active biological systems with similar self-organization.
% insert abstract here
\end{abstract}

@@

\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
Janus particles (JPs) are colloids with two surfaces of different
properties.
For example, it is common for the surface of a Janus particle to
be partly hydrophilic and hydrophobic (polar and non-polar).
In a viscous solvent, Janus particles often self-assemble into
structures with tunable functions for biomedical engineering
applications
\cite{
  GheisariSahfieeAbbasiEtAl2021_DMR,
  LiuYangHuangEtAl2016_Angew,
  LiWangYaoEtAl2019_Nanoscale,
  Bradley2016}.
Depending on the interactions between Janus particles and the surrounding viscous solvent,
JPs self-assemble into oligomers of various geometries and sizes\cite{Bradley2017}.

Dynamics offers yet another dimension of control that emerges naturally
from the interactions between particles and fluid in colloidal matter \cite{Brandner2019,RevModPhys.93.025008}.
Active colloidal systems show nonequilibrium self-organization with
complexity rivaling that of biological systems such as living cells,
bacterial baths, and animal flocks\cite{CollardGrosjeanVandewalle2020,Vutukuri2020}.
A long-standing challenge in fluid mechanics
and material science is to solve the ``inverse" problem of creating a model
colloidal system that will self-assemble into a prescribed structure
\cite{PhysRevLett.128.256102}.
For example, the framework of geometrical frustration, which has been
used to explain disordered systems, could be used to design new, ordered systems
instead, through specific choices for the shapes or interactions of the particles
\cite{Manoharan2015_Science}.

The many-body hydrodynamics of amphiphilic Janus particles (JP)
assembled as vesicles and suspended
in a viscous fluid (at zero Reynolds number) has been studied using
boundary integral numerical simulations \cite{Fu20,Fu2022_JFM}.
The dynamics of the JP suspension results from the combination
of long-range hydrodynamic interaction and non-local
interactions between JPs through the distribution of
a hydrophobic attraction potential (HAP).

In a quiescent flow, numerical simulations of a 
JP suspension showed self-assembly into micelles and bilayers of
JPs that provide an alternative means for computing the 
mechanical moduli of a colloidal membrane \cite{NaTr00,Fu20,KrFiGuKaHa13}.
Under background flows, the hydrodynamics of a JP vesicle (a
self-enclosed bilayer of JPs) exhibit many familiar behaviors of a
vesicle \cite{Fu2022_JFM}: 
elongation and alignment along the extensional direction, tank-treading,
and rupture of a vesicle under shear flow.

In this work we take advantage of the flexibility of the model to examine the
effects of boundary condition on JP surfaces that could be controlled
based on the chemicals used in the experiments, for example.
It turns out that a simple tuning of the hydrophobic distribution
leads to multilamellar and striated structures. 
Here less is understood about the flow-structure interactions
and we investigate the
deformation of these novel materials in background flows
and map out their collective behavior away from equilibrium.

@@

Without inertia, $(\uu, p)$ also satisfy the force-free and torque-free conditions.
This means that the force and torque from the hydrodynamic stress on each particle 
are in balance with the total
force and torque coming from the hydrophobic potential and repulsion.
To compute this balance, we define
the free energy\cite{Ma77, GoHaKo94, Fu20, Fu2022_JFM}
\begin{equation}
\label{eq:free_energy}
F = \gamma
\int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
\end{equation}
where $u(\xx,t)$ is as an order parameter for the structure of water,
$\rho$ is a decay length, and $\gamma$ is an interfacial tension.

The order parameter $u(\xx,t)$ is assumed to the minimizer of the free energy $F$.
Its governing equations $u(\xx,t)$ are a screened Laplace equation boundary value problem
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  \label{eq:SLbc}
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
The boundary condition $g$ encodes hydrophobic properties of the
particle-solvent interface.

@@

To get the force $\FF_i$ and torque $T_i$ on $\Gamma_i$ from the free energy\cite{Fu20},
we compute the variation of the domain of the free energy 
\eqref{eq:free_energy} subject to \eqref{eq:SL}-\eqref{eq:SLbc},
and obtain 
\begin{equation}
  \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
  - \frac{M}{\rho_0}
  \sum_{j \neq i}
  \frac{\aa_i - \aa_j}{|\aa_i - \aa_j|}
P'\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right)
  ,\quad
T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
\end{equation}
for $i = 1,\dots,N_b$ with particle outward normal $\nu$. The term 
$
\mathbf{T}
= \gamma \left[ \rho^{-1} u^2 \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
$
is the hydrophobic stress.
Repulsion is rotationally symmetric and does not contribute to the torque.

@@

In BC (ii) with $b = 1$, the boundary data is everywhere positive.
It takes the maximum value $3a$ on the tail (red) and the
minimum value $a$ on the head side (yellow). 
Both sides of the Janus particle are hydrophobic but
more so on the $\alpha = 0$ side.  
Over a short time scale, these particles also self-assemble into bilayers. But unlike for  (i),
the heads are also hydrophobic and so in the long-time dynamics
these bilayers form multilamella structures\cite{C9NR05885K}.
The number of folds depends primarily on the number of particles.
Fig~\ref{fig:relax}(c), for example, shows a
multilamellar structure with four layers and one with two layers in the inset.

@@

To measure positional order, we use a number,
which we call the strain parameter, 
\begin{equation}
\label{eq:SP}
E = \frac{1}{N_b} \sum_{i=1}^{N_b}
\|\tfrac{1}{2}(\mathsf{F}_i^T \mathsf{F}_i - I)\|
\end{equation}
where $\mathsf{F}_i$ is an 
approximate deformation gradient at particle $i$.
The argument inside the Frobenius norm $\| \cdot \|$
is the Green-Lagrange strain tensor.
The motivation for  \eqref{eq:SP} is as follows.
For relatively weak background flow strengths, the near-equilibrium particle
configurations behave as an elastic solid.  There is a map $\ff(\xx,t)$
from the reference (equilibrium) configuration with $\ff(\aa_i(0),t) = \aa_i(t)$
for $i = 1,\dots,N_b$.  Using linear approximation,
\[
\aa_j(t) - \aa_i(t) = \ff(\aa_j(0),t) - \ff(\aa_i(0),t)
\approx \nabla \ff(\aa_i(0),t)(\aa_j(0) - \aa_i(0)).
\]
To approximate
the deformation gradient $\nabla \ff(\aa_i(0),t)$
we solved the overdetermined system 
\[
\aa_j(t) - \aa_i(t) = \mathsf{F}_i(\aa_j(0) - \aa_i(0)),\quad j = 1,\dots, N_b  
\]
for $\mathsf{F}_i$ by weighted least squares. The weights  
$w_i = \exp(-\|\aa_j(0) - \aa_i(0)\|/4c)$ with particle radius $c$
ensure that the linear approximation is valid for
particles near $\aa_i$.

@@

\section{Results}
\label{sec:results}
In this section, we subject the Janus particle structures to various background
flows.  The purpose is to understand how self-assembled particles
respond to external forcing.
We can then compare effective properties of
materials comprised of Janus particles as a function
of their amphiphilic properties.  
%%%

@@

%%%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure4.pdf}
  \end{center}
  \caption{
    \label{fig:Ves_shear}
The figure shows a single vesicle in a shear flow. Panels (a)-(c) are snapshots for $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
The streamlines are plotted in the background.
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
     }
\end{figure}
%
\citet{Fu2022_JFM} studied the hydrodynamics of a JP vesicle under a linear shear flow. 
Focusing on drawing analogies to hydrodynamics of a vesicle in continuum modeling
(such as tank-treading \cite{keller_skalak_1982,Finken08,Shaqfeh11}, bilayer slip \cite{sch-vla-mik2010,denOtter2007,Zgorski2019}, and permeability \cite{chabanon2017,qua-gan-you2021}),
our previous studies showed the existence of a critical shear
rate above which the JP vesicle ruptures
\cite{grandmaison_brancherie_salsac_2021,D2SM00179A}. 
Based on the these early results, we
reinitialized the BC (i) configuration
in the form of a single, circular vesicle (rather than several bilayer components)
and illustrate how the three measures of structural deformation 
correlate to the dynamics of a JP vesicle.

@@

We calculated the vesicle area $A$ and length $L$ (initial area $A_0$, initial length $L_0$)
by averaging the area/length for the inner and outer leaflets.  
As shown in Fig~\ref{fig:BTG_Scale}(e),
the relative area $A/A_0$ decreases during the simulations, with a rate
depending nonmonotonically on $l$.  
The relative length $L/L_0$, however, is constant in $t$ for all cell sizes (Fig~\ref{fig:BTG_Scale}(e), inset).
This implies that the vesicle behaves as an inextensible, permeable membrane.
In previous work, \cite{Fu2022_JFM} determined the permeability constant of particle-based vesicles
in the context of shear background flow\cite{chabanon2017,qua-gan-you2021}.

@@

\section{Discussion}
Our results were for $N_b = 60$.  This particle number was large enough for the JP to form
measurable structures while giving managable simulation times (days) on a single computing processor.
The simulation time for $N_b = 198$ in Fig. \ref{fig:relax} and Fig. \ref{fig:relax_energy}
was several weeks, and so we avoided simulations of this size for our results.
We used $N = 16$ grid points per particles for all simulations.  We performed a convergence study
and found that using $N = 16$ or $N = 24$ grid points per particle gave quantitavely indistinguishable
results.  The time courses consisted of $O(10^3)$ time steps with $\Delta t = 0.2$ nm.

@@

In terms of fluid behavior,
the multilamellar (BC (ii)) structure behaves as shear thinning fluid
while the striated structure (BC (iii)) has a finite yield stress. 
Qualitatively, the strains for BC (ii) increases gradually 
with shear rate (Fig~\ref{fig:BC2_shear}(f)).
In contrast, the strains for BC (iii) are constant over a range of flow strengths
and then increase when the flow strengths are large enough
to deform the body (Fig~\ref{fig:BC3_shear}(f)).
To quantify this behavior, we form 
\[
\mu_{\text{sus}} = \frac{\dot \gamma}{\dot E} \mu
\]
as an effective dynamic viscosity of the suspension.
The numerator $\dot \gamma \mu$ gives the force per area provided by the solvent stresses. 
The strain rate $\dot E$ of the body is the slope of a linear fit to the strain curves e.g.,
in Fig~\ref{fig:BC2_shear}(f).

Calculated suspension viscosities are shown
in Table \ref{tbl:bcii_visc}.
The middle row gives the solid area fraction $\phi$;
the sum of the rigid particle areas divided by the
total area of the solvent and particle region.
We observe that for the multilamellar structure,
$\mu_{\text{sus}}$ is decreasing
with increasing shear rate.
The predicted suspension viscosities 
are on the order of hundreds of times that of water,
consistent with measurements of noninteracting
particle suspensions\cite{KONIJN201461}.
In the case of striated structures, viscosity is
effectively infinite for the lower two of the shear rates,
and then drops to a finite value $\mu_{\text{sus}} = 60$ mPa s
when the shear rate reaches $0.15$ ns$^{-1}$.
\begin{table}
  \caption{Suspension viscosity $\mu_{\text{sus}}$ (mPa s) 
\label{tbl:bcii_visc}
}
\centering
\begin{tabularx}{0.7\textwidth}{c|X|X|X||X|X|X}
&\multicolumn{3}{c||}{BC (ii)} & \multicolumn{3}{c}{BC (iii)}\\
\hline
  $\dot \gamma$ & 0.05 & 0.10 \quad & 0.15 & 0.100 & 0.125 & 0.15\\
  \hline
  $\phi$ & 0.50 & 0.47 & 0.41 & 0.47 & 0.46 & 0.45 \\
  \hline
  $\mu_{\text{sus}} $ & 401 & 66 & 42 & 2.5e3 & 1.4e3 & 60\\
\hline
\end{tabularx}
\end{table}

We have not calculated suspension viscosities for the type (i) boundary condition,
because the viscosities of bilayer are in-plane and require fully three-dimensional
simulations to resolve\cite{denOtter2007,Zgorski2019,doi:10.1073/pnas.2100156118}.  Our previous work 
did calculate, however, an intermonolayer friction coefficient $b$
which is related but conceptually different than viscosity \cite{Fu2022_JFM}.

While increased flow strengths generally injected energy into the suspension,
the simulation results show that the unstructured bilayer 
actually increases orientational order and has somewhat lower free energy 
under low shear rates (Fig~\ref{fig:BC1_shear}(d,f)).
This effect suggests that in amphiphilic suspensions,
it might be possible decrease the excess area of the system 
by subjecting the suspension to a moderate shear flow.
Not all background flows produce this ``organizing'' effect, as it was not
observed in the TG background flow case (Fig~\ref{fig:BC1_TG}).
\citet{PhysRevLett.128.256102} have shown how to drive particle clusters into arbitrary target shapes by solving
a first passage problem.

@@

The characteristics of the self-assembly of amphiphilic JP into onion-like
dendrimersomes have been studied
by molecular dynamics simulations\cite{C9NR05885K}.  
The molecular dynamics simulations
use an anisotropic pair potential
is used to describe the particle interactions
where a harmonic form describes the repulsive part 
and an anisotropic attractive part describes the hydrophobic interactions.
\section{Conclusion}

\label{sec:conclusion}
